## Evolutionary History of Siphonophore Biology

### 2017-02-21 character_coding/CharacterEvolution.Rmd
added pGLS.Ives for dummy coded sex

>>>>

###PGLS
```{r pgls_depth_sex, echo=F, message=F, warning=F}
dp_sex <- dpruned_data$Sex
dp_sex = as.numeric(dp_sex)
names(dp_sex) = names(depth_median)
dp_sex[dp_sex==2] = 0        # 0 = Monoecious, 1 = Dioecious
#Vx <- Vy <- Cxy <- rep(0,length(dpruned_tree$tip.label))
#pgls.Ives(dpruned_tree, dp_sex, depth_median, Vx, Vy, Cxy)
pGLS = pgls.Ives(dpruned_tree, rep(dp_sex,3), rep(depth_median,3))
gls(dp_sex ~ depth_median)
```
